Results

### 2024-08-15 analysis/results.Rmd
Journal database coverage: Upset by publisher

```{r upset_data}
cr_active_upset <- cr_df |>
  filter(issn_l %in% active_jns$issn_l) |>
  group_by(issn_l) |>
  summarise(n_cr = n_distinct(doi)) |>
  mutate(crossref = TRUE)
wos_active_upset <- wos_active_core |>
  group_by(issn_l) |>
  summarise(n_wos = n_distinct(item_id)) |>
  mutate(wos = TRUE)
scp_active_upset <- scp_active_core |>
  group_by(issn_l) |>
  summarise(n_scp = n_distinct(item_id)) |>
  mutate(scopus = TRUE)

jn_upset_ <- dplyr::full_join(cr_active_upset, wos_active_upset, by = "issn_l") |>
  dplyr::full_join(scp_active_upset, by = "issn_l") |>
  mutate(across(c(crossref, wos, scopus), ~replace_na(.x, FALSE))) |>
  # Journal 5-years article volume
  mutate(n = case_when(!is.na(n_cr) ~ n_cr, !is.na(n_scp) ~n_scp, TRUE ~ n_wos))

@@

jn_upset <- jn_upset_ |>
  inner_join(jn_age, by = "issn_l")
library(ComplexUpset)

ComplexUpset::upset(
  jn_upset,
  c("crossref", "wos", "scopus"),
  base_annotations = list(
    `Journals` = (
      intersection_size() +
        scale_y_continuous(labels =  scales::number_format(big.mark = ","))
    )
  ),
  annotations = list(
    'Article Volume' = (
      ggplot(jn_upset, aes(x = intersection, y = n)) +
        geom_boxplot(outliers = FALSE) +
        scale_y_log10(labels =  scales::number_format(big.mark = ",")) 
    ),
    # journal age, not very useful
    'Journal age' = (
      ggplot(jn_upset, aes(x = intersection, y = jn_age)) +
         geom_violin())
    )
  )
```

>>>>

```{r upset_data, fig.asp=0.8}
cr_active_upset <- cr_df |>
  filter(issn_l %in% active_jns$issn_l) |>
  group_by(issn_l) |>
  summarise(n_cr = n_distinct(doi)) |>
  mutate(Crossref = TRUE)
wos_active_upset <- wos_active_core |>
  group_by(issn_l) |>
  summarise(n_wos = n_distinct(item_id)) |>
  mutate(WoS = TRUE)
scp_active_upset <- scp_active_core |>
  group_by(issn_l) |>
  summarise(n_scp = n_distinct(item_id)) |>
  mutate(Scopus = TRUE)

jn_upset_ <- dplyr::full_join(cr_active_upset, wos_active_upset, by = "issn_l") |>
  dplyr::full_join(scp_active_upset, by = "issn_l") |>
  mutate(across(c(Crossref, WoS, Scopus), ~replace_na(.x, FALSE))) |>
  # Journal 5-years article volume
  mutate(n = case_when(!is.na(n_cr) ~ n_cr, !is.na(n_scp) ~n_scp, TRUE ~ n_wos))

@@

# Add Esac publisher

esac <- hoaddata::jct_hybrid_jns |>
  distinct(issn_l, esac_publisher) |>
  mutate(
    publisher = case_when(
      esac_publisher == "Elsevier" ~ "Elsevier",
      esac_publisher == "Springer Nature" ~ "Springer Nature",
      esac_publisher == "Wiley" ~ "Wiley",
      is.character(esac_publisher) ~ "Other"
    )) |>
  mutate(publisher =
           forcats::fct_relevel(
             publisher,
             c("Elsevier", "Springer Nature", "Wiley", "Other") 
           )) |>
  mutate(publisher = forcats::fct_rev(publisher)) |>
  distinct(issn_l, publisher)

library(ComplexUpset)
jn_upset <- left_join(jn_upset_, esac, by = "issn_l")

size = get_size_mode('exclusive_intersection')

ComplexUpset::upset(
  jn_upset,
  c("Crossref", "WoS", "Scopus"),
  # Only journals in Crossref
  min_size = 30,
  width_ratio = 0.4,
  stripes = "transparent",
  name = "Data Source Coverage",
  base_annotations = list(
    "Journals" = (
      ComplexUpset::intersection_size(
        counts = TRUE,
        text = list(size = 9 / .pt),
        text_mapping = aes(
          label = paste0(!!upset_text_percentage(), '\n(', !!size, ')'),
          colour = ifelse(!!size > 5000, 'on_bar', 'on_background'),
          y = ifelse(!!size > 5000, !!size - 4000, !!size)
        )
      ) +
        scale_y_continuous(labels = scales::number_format(big.mark = ","))
    )
  ),
  annotations = list("Article Volume" = (
    ggplot(mapping = aes(x = intersection, y = n, fill = fct_rev(publisher))) +
      geom_boxplot(outliers = FALSE) +
              scale_fill_manual(
        "",
        values = c(
          "Elsevier" = "#e9711c",
          "Springer Nature" = "#486a7e",
          "Wiley" = "#068853",
          "Other" = "#b3b3b3a0"
        ), guide = "none") +
      scale_y_log10(labels =  scales::number_format(big.mark = ","))),
    "Publisher" = (
      ggplot(mapping = aes(fill = publisher)) +
        geom_bar(stat = "count", position ="fill") + 
        scale_y_continuous("Publisher Share", labels=scales::percent_format()) +
        scale_fill_manual(
        "",
        values = c(
          "Elsevier" = "#e9711c",
          "Springer Nature" = "#486a7e",
          "Wiley" = "#068853",
          "Other" = "#b3b3b3a0"
        ), guide = "none"))), 
  #,
  # 'Total article' = (
  #   ggplot(mapping = aes(x = intersection, y = n)) +
  #     geom_bar(stat = "identity", color = "grey35", fill = "grey35")) +
  #  scale_y_continuous(labels =  scales::number_format(big.mark = ",")) ),
  set_sizes=(
        upset_set_size(
          geom = geom_bar(aes(fill = publisher), width = 0.8), 
          position='right')) +
          scale_fill_manual("", values = c(
          "Elsevier" = "#e9711c",
          "Springer Nature" = "#486a7e",
          "Wiley" = "#068853",
          "Other" = "#b3b3b3a0")) +
    scale_y_continuous(labels = scales::number_format(big.mark = ",")) +
    guides(fill = guide_legend(reverse = TRUE)) +
    ylab("Journals"),
      guides = "over",
  matrix = (
        intersection_matrix(
            geom = geom_point(
                shape = "square",
                size=3.5
            )))
        ) +
  patchwork::plot_layout(heights=c(2, 1.5, 2, 1))
```
